Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
remis removed part

 \smallskip\noindent
 \[  OT_1  = \openrule{
      \{P\mapsto p\_send(m)\} \qquad [m=m'] \qquad \{s1\_m\gets m\}
                      }
    {\ostate{s_0,a_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,a_0,r_0}}
    \]

@@

\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}.

%\TODO{:  and maybe one example on the Impl. OTs presented in latex readable form??}
\TODO{Comment on Fig 3...}

\begin{figure}[t]
   \centerline{\includegraphics[width=9cm]{ATG/SPSpecOpen}}
   \caption{Specification OA (version with the error counter)}
   \label{SimpleProtCounter:SpecOA}
\end{figure}

Figure \ref{SimpleProtCounter:ImplOA} shows the full open automaton of the implementation $SimpleSystem$. Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule. Note that the resulting action of the OTs appear here betwen the guard and the set of assignments.
Note that we have also simplified the form of the variable dependencies in the OTs, again for readability, replacing e.g. in OT1 $\{P\mapsto p\_send(m)\} \qquad [m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.

>>>>

 \smallskip\noindent
 \[  OT_1  = \openrule{
      \{P\mapsto p\_send(m)\},  [m=m'],  \{s1\_m\gets m\}
                      }
    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,m_0,r_0}}
    \]

@@

\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
\RAB{Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule. Note that the resulting action of the OTs appear here between the guard and the set of assignments. For example, in the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=P\_a\neq p\_send$, and $\alpha=P\_a$ is denoted in the open automata \texttt{\{P->p-a\} [P-a!=p-send] P-a}.
}

\begin{figure}[t]
   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
   \caption{Specification OA (version with the error counter)}
   \label{SimpleProtCounter:SpecOA}
\end{figure}

Figure \ref{SimpleProtCounter:ImplOA} shows the full open automaton of the implementation $SimpleSystem$. Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule. Note that the resulting action of the OTs appear here betwen the guard and the set of assignments.
Note that we have also simplified the form of the variable dependencies in the OTs, again for readability, replacing e.g. in OT1 $\beta=\{P\mapsto p\_send(m)\}$ $\Pred=[m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.
